---
title: "Developer Course"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Developer Course}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

This document gives an outline of concepts relevant to the development of the community package.
Each section presents questions or exercises to consider.

# Data Background

## Data Alignment

1. What is the value of `value` in 2015?

```{r}
data.frame(value = c(1, 2, 3), year = c(2012, 2013, 2014))
```

Answer: `NA`, the year 2015 does not exist in this data frame

2. What is the mean absolute error between the `value`s of `d1` and `d2`?

```{r}
(datasets <- list(
  d1 = data.frame(value = c(1, 2, 3), year = c(2012, 2013, 2014)),
  d2 = data.frame(value = c(1, 2, 3), year = c(2013, 2014, 2015))
))
```

```{r}
d3 <- data.frame(
  year = c(2012, 2013, 2014, 2015),
  value_d1 = c(1, 2, 3, NA),
  value_d2 = c(NA, 1, 2, 3),
  ae = c(NA, 1, 1, NA)
)
```
Answer: MAE = `r mean(d3$ae, na.rm=TRUE)`


## ID Mapping

1. If prefix `123` is selected, which rows should be included?

```{r}
data.frame(ID = c(1234, 1243, 1235, 1245))
```
Answer: rows 1 (1234) and 3 (1235)

2. We aggregate the `lower` data frame, using mean function, and grouping the data by ID prefix and time as given in the `higher` data frame

```{r}
(datasets <- list(
  higher = data.frame(
    ID = c(123, 124, 123, 124),
    time = c(1, 1, 2, 2)
  ),
  lower = data.frame(
    ID = c(1234, 1243, 1235, 1245, 1234, 1243, 1235, 1245),
    time = c(1, 1, 1, 1, 2, 2, 2, 2),
    v1 = c(10, 5, 20, 13, 7, 15, 18, 23),
    v2 = c(1, NA, 3, NA, 5, NA, NA, NA)
  )
))
```

Aggregated `higher`:
```{r}
datasets$higher[, 3:4] <- do.call(rbind, lapply(
  split(datasets$lower[, -2], datasets$lower$time), function(d) {
    do.call(rbind, lapply(
      split(d[, -1], substring(d$ID, 1, 3)), colMeans,
      na.rm = TRUE
    ))
  }
))
datasets$higher[is.na(datasets$higher)] <- NA
datasets$higher
```

# R Packaging Background

## Documentation

Edit the description of the `dir` argument of the `site_build` function.

2. How would you get that change to appear in the local R help (`?site_build`)?

3. How would you get that change to appear on the documentation site ([site_build.html](https://uva-bi-sdad.github.io/community/reference/site_build.html))?

## Debugging

Without editing any code, calculate the row means of `cols` after it has been updated in

```r
util_make_palette(rep(c("red", "green", "blue"), each = 10), polynomial = TRUE)
```

Expected result:
```{r}
c(red = 102, green = 51, blue = 102)
```

## Testing

Write a test to cover the first uncovered line of the `datacommons_refresh` function.

1. How would you update the coverage report?

# JavaScript Background

## Editing Source

- Add a line of code that will log to the console whenever a dataset is loaded.
  1. How would you see if it works?
  2. How would you push that change out to a live site?

- There is functionality to display information about a variable when its name is clicked on.
Change that display to show a piece of information that isn't currently being shown.
  1. How would you see what information is available?

## Testing

Take a look at the coverage of the `data handler > checks > value_checks` object,
and note that some functions are not covered (such as `!=`).

Write a test to cover one of those functions.

1. How would you update the coverage report?

2. How would you trigger that function in a browser console?
